Open Policing Project: Prima Facie Stats

### 2019-01-25 lib/bunching_report.Rmd

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(
  tbl,
  division,
  hour_of_day,
  age_group,
  vehicle_make,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(
  tbl,
  region,
  hour_of_day,
  vehicle_type,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(
  tbl,
  hour_of_day,
  vehicle_make,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

>>>>

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_clean_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(
  tbl,
  division,
  hour_of_day,
  age_group,
  vehicle_make,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_clean_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(
  tbl,
  region,
  hour_of_day,
  vehicle_type,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_clean_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(
  tbl,
  hour_of_day,
  vehicle_make,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```
